Freezing of a Weeks-Chandler-Anderson Fluid using classical Density Functional Theory

### 2020-10-29 papers/thesis-kirstie/thesis.tex
edits

Classically, fluids have been modeled by a collection of small, 
impenetrable spheres colliding with one another like billiard balls. 
In the simplest case, the spheres are treated as having only a replulsive 
potential. This model, called the Hard-Sphere fluid, has served as the 
primary reference system for fluids. This is due to the fact that the 
repulsion between atoms is much stronger than their attraction, and so 
the repulsive potential, which is descriptive of hard spheres, dominates 
the interactions between atoms. In 1954 Zwanzig introduced the Square-well 
fluid which is a perturbation of the Hard-Sphere fluid created by adding 
a hard-edge attractive potential to the repulsive potential of the 
Hard-Sphere fluid~\cite{ZwanzigSqrWell}. In 1964 Rowlinson studied 
spheres with softly fading replusive potentials which he modeled by making
the radius of the spheres temperature dependent~\cite{rowlinson1964statistical}. 
This reflects the idea that soft-spheres penetrate more deeply into 
each other when they collide at higher temperatures.

In 1967 Barker and Henderson combined the perturabtion approach of Zwanzig 
with Rowlinson's idea of using temperature-dependent radii to model spheres 
with soft repulsive potentials to create the Barker-Henderson model 
fluid~\cite{barker1967perturbation}, where a soft-sphere fluid by is 
modeled by using a Hard-Sphere fluid with hard spheres of larger radii 
at low temperatures, and smaller radii at high temperatures. In 1971 Weeks, 
Chandler, and Anderson used temperature and density dependent hard-sphere 
radii to model spheres with the more realistic softly fading repulsive 
portion of the Leonard-Jones potential~\cite{andersen1971relationship}, 
which is known as the Weeks-Chandler-Anderson model fluid.

While models for particular fluids were being created, powerful methods 
to describe the properties of fluids in general were also being developed. 
In the late 1950s, Scaled Particle Theory (SPT)~\cite{ReissSPT} was 
introduced from which an equation of state, and an expression for the 
excess Helmholtz free energy of a homogeneous Hard-Sphere fluid can be 
obtained~\cite{Hansen}. \color{red}ADD Percus-Yevick introduced an 
alternative method...OZ... \color{black}
%Percus and Yevick took another approach to the Hard-Sphere fluid.
In 1961 Morita and Hiroike introduced a density functional 
approach~\cite{MoritaDFT} to finding the equilibrium grand free energy 
(the equilibrium Helmholtz free energy in the case of a canonical 
ensemble), and the cooresponding equilibrium number density profile for 
inhomogeneous fluids. To use this approach, a functional must be 
constructed for a particular fluid.
%DFT Evans 1979
%Led by the consistency bewteen results from SPT and Percus-Yevick, 
In 1989 Rosenfeld introduced Fundamental Measure Theory (FMT)~\cite{rosenfeld1989} 
(which can be constructed from SPT~\cite{santos2012phi3}) to form a 
functional for the Hard-Sphere fluid. Tarazona later improved on the 
method by introducing a tensor version of the functional~\cite{tarazonaphi3, 
santos2012phi3}, and in 1999 Schmidt adopted FMT for soft spheres 
forming Soft Fundamental Measure Theory (SFMT)\cite{schmidt1999density}.

Schmidt applied his Soft Fundamental Measure Theory to various fluids 
with soft repulsive and soft attractive potentials, and developed an erf 
model for spheres with steep, short-range soft repulsive 
potentials~\cite{schmidt2000fluid}. In this paper, Density Functional 
Theory (DFT) will be used to predict the freezing of a Weeks-Chandler-Anderson 
model fluid by applying SFMT with Schmidt's proposed erf model, and our temperature
dependent parameters to form the functional for the excess Helmholtz free energy. 
%for generating the weight funcions, and Tarazona's tensor functional. 
Results will be compared to those generated from Monte-Carlo simulations.

@@

\section{Overview}
We use classical Density Functional Theory (cDFT) in conjunction 
with Soft Fundamental Measure Theory (SFMT) to find the equilibrium free 
energy of a system, and the corresponding equilibrium number density profile. 
In particular, SFMT is used to form the expression for the excess Helmholtz 
free energy without having to take into account the interaction each sphere, 
or atom, has with every other sphere. The excess free energy is then added 
to the ideal free energy calculated analytically to find the resulting 
free energy for the system. 
\begin{equation}{F=F_{ideal} + F_{excess}}\end{equation} 
For a spatially varying number density, as would be expected for a crystal, 
the free energy is a functional of the number density profile $n(\vec{r})$  
\begin{equation}{F[n(\vec{r})]=F_{ideal}[n(\vec{r})] + F_{excess}[n(\vec{r})]}\end{equation}

To implement cDFT, the number density profile $n(\vec{r})$ is varied with 
the temperature fixed until the free energy is minimized. The minimum free 
energy and its corresponding number density profile are then the equilibrium 
values for that temperature. Once the Helmholtz free energy for both the crystal and liquid states of 
the fluid are found, they can be compared to find the resulting state of 
the fluid. Outside the region of coexistence, the fluid will be completely 
in a crystalline state if the crystal free energy is lower than the liquid 
free energy, and it will be completely in a liquid state if the liquid 
free energy is lower than the crystal free energy.

@@

In general, if at some number density and temperature the crystal free energy 
is lower than the homogeneous free energy of the liquid then the fluid will 
be in the crystalline state. If the crystal free energy is higher than 
the homogeneous free energy, then the fluid will be in the liquid state. 
However, there is a region of densities between the liquid and crystal 
states that are forbidden, and so the actual state can not be determined 
just by which energy is lower at that particular number density and
temperature. Maxwell's Double Tangent Construction must be implemented 
using the date collected to determine the actual crystal and liquid states, 
and construct phase diagrams.

@@

\section{Our Functional for the Excess Helmholtz free energy}

%The excess Helmholtz free energy is particular to the fluid being modeled, 
%as it depends on the interatomic potential V(r). 
We use Soft Fundamental Measure Theory to find the excess Helmholtz free energy.
The functional is written in general form as 
\begin{align}
  F_{excess}[n(\vec{r})]=k_BT\int(\Phi_1(\vec{r})+\Phi_2(\vec{r})+\Phi_3(\vec{r}{)) d}\vec{r}
\end{align}
where
\begin{align}
\Phi_1 &= -n_{0}\ln(1-n_{3}) \\
\Phi_2 &= \frac{n_{1}n_{2}-\vec{n_{1}}\cdot\vec{n_{2}}}{1-n_{3}} \\
\Phi_3 &= \frac{{n_2}^3-3n_2\vec{n}_{v2}\cdot\vec{n}_{v2}+\frac{9}{2}[\vec{n}_{v2}\cdot{\overleftrightarrow{n}_{m2}}\cdot{\vec{n}_{v2}}-\operatorname{Tr}({\overleftrightarrow{n}^3_{m2}})]}{24\pi(1-n_3)^2}  
\end{align} 
and Tarazona's tensor expression~\cite{tarazonaphi3, santos2012phi3} is used 
for $\Phi_3$. The weigthed densities $n_0, n_1, n_2,$ and $n_3$ are found from
\begin{equation}{n_i(\vec{r})=\int_{Volume}{n(\vec{r'})w_i(|\vec{r}-\vec{r'}|)d{\vec{r'}}}}\end{equation}
where the number density profile $n(\vec r)$ within the integral is given by a Gaussian function,
%\begin{align}
  %n(\vec r)=(1-f_v)\frac{\exp^{-\frac{r^2}{2{\sigma}^2}}}{\left(\sqrt{2\pi}\sigma\right)^3}
%\end{align}
and the weight functions $w_0, w_1, w_2,$ and $w_3$ are given by
\begin{align}\label{eq:weights}
  w_{0}(r) &=\frac{w_{2}}{4\pi{r}^2} \\
  w_{1}(r) &=\frac{w_{2}}{4\pi{r}} \\
  w_2(r)&=\frac{\sqrt{2}}{\Xi\sqrt\pi}\exp^{-\left(\frac{r-\frac{\alpha}{2}}{\Xi/\sqrt{2}}\right)^2}
  \\
  w_3(r)&=\frac{1}{2}\left[1-\operatorname{erf}\left(\frac{r-\frac{\alpha}{2}}{\frac{\Xi}{\sqrt{2}}}\right)\right]
\end{align}
The weight fucntions $w_{2}(r)$ and $w_{3}(r)$ are constructed using 
Schmidt's proposed erf model~\cite{schmidt2000fluid} in which he set
\begin{equation}{w_3(r)=\frac{1}{2}}\left[1-\operatorname{erf}\left(\frac{r-\frac{\sigma}{2}}{\frac{\text{a}}{\sqrt{2}}}\right)\right]\end{equation} 
where $w_3(r)$ is subject to the boundary conditions $w_3(0)\approx{1}$ 
and $w_3(\infty)=0$. 
%\color{red}These boundary conditions are satisfied for $\Xi{\sqrt{2}<<\alpha}$, or $k_BT << 2.21$. \color{black} 
Our functional is  created by replacing Schmidt's parameters $\sigma$ 
and $a$ with our temperature dependent parameters $\alpha(T)$ and $\Xi(T)$.
\begin{equation}\sigma = \alpha(T)\text{~~~~~~~and~~~~~~~} a = \Xi(T)\end{equation}

@@

The result can be made more accurate by increasing NumPoints which is the 
number of vectors randomly generated. In order to further reduce the error 
in the average, antithetic variates are used. Rather than computing an average 
of a set of random points, each random point in the set is paired with a 
point along the same line as the first point, but opposite in direction, 
as shown in Figure \ref{fig:AntitheticVariate}. This reduces first order 
error in the average by filtering out an erroneous offset of values along 
the line connecting the two points by averaging the two results, one of 
which may be erroneously higher than it should be while the other is 
erronesously lower than it should be.

 \begin{figure}[h!]
    \centering
    \includegraphics[height=4cm]{AntitheticVariate.png}
    \caption{Antithetic variates reduce first order error in an average. 
    Each point in the average is paired with another point from along 
    the same line as the first, and at an equal, but opposite distance.}
    \label{fig:AntitheticVariate}
  \end{figure} 
Incorporating antithetic variates $-\vec{dr}$ for every $\vec{dr}$ equation ?? becomes:
\begin{displaymath}{n_i(\vec{r}_k, \vec{R}_j)=\sum_{NumPoints}\frac{1}{2}\frac{(1-f_v)\left[w_i(|\vec{r}-\vec{R_j}-\vec{dr}|) +w_i(|\vec{r}-\vec{R_j}+\vec{dr}|)\right]}{NumPoints}}\end{displaymath}   The process is repeated for all the other $\vec{R}_j$'s to get the total weighted densities at vector $\vec{r}_k$ due to all the Gaussians. 
\begin{displaymath}{n_i(\vec{r}_k)=\sum_j{n_i(\vec{r}_k, \vec{R}_j)}}\end{displaymath}
Then the entire process repeated for each vector $\vec{r}_k$ to get the 
total weighted densities $n_i(\vec{r})$ as a function of the position $\vec{r}$.

The standard error of the mean (SEM) is given by:
\begin{equation}{SD_{mean}=\frac{SD}{\sqrt{N}}}\end{equation} which gives 
a measure of the error in $n_3=\overline{w}_3$:
\begin{equation}{Error=\sqrt{\frac{\overline{w_3^2}-(\overline{w}_3)^2}{NumPoints}}}\end{equation} 
NumPoints, the number of vectors randomly generated, is increased until:
\begin{equation}{Error<\frac{|1-n_3|}{4}}\end{equation} where the maximum 
value that $n_3$ can be without error is 1.

Figure \ref{fig:GaussandW2_actual} ......

 \begin{figure}[h!]
    \centering
    % FIXME \includegraphics[height=6cm]{GaussandW2_actual.png}
    \caption{A Gaussian centered at $\vec{R}$ is shown in blue, and a cross-sectional 
    view of $w_2$ centered at $\vec{r}'$ is shown in purple. Here, the weight function 
    is evaluated at $\vec{r}-\vec{r}'$ where $\vec{r}'=\vec{R}+\vec{dr}$ and $\vec{dr}$ 
    is generated randomly according to a Gaussian distribution.} 
  \label{fig:GaussandW2_actual}
  \end{figure}

 \begin{figure}[h!]
    \centering
    % FIXME \includegraphics[height=6cm]{GaussandW2_thinkas.png}
    \caption{An alternative way of viewing Figure \ref{fig:GaussandW2_actual} where 
    the weight function, shown by the purple dashed lines, is centered at $\vec{r}$  
    and fixed in place as $\vec{dr}$ varies randomly.} 
  \label{fig:GaussandW2_thinkas}
  \end{figure}

@@

\begin{figure}
  \centering
  \includegraphics[width=\columnwidth]{figs/Phase_Diagram_of_T_vs_n_AS}
  %\includegraphics[height=10cm]{figs/Phase_Diagram_of_T_vs_n_AS}
  \caption{Phase Diagram of the reduced temperature verses the reduced density for the WCA fuild. 
  White lines show the liquid and solid transition densities at each temperature from 
  simulations of a WCA fluid by Ahmed and Sadus~\cite{ahmedsadus}. The gray region is the region of coexistence.}
  \label{fig:Phase_Diagram_of_T_vs_n_AS}
\end{figure}

@@

\begin{figure}
  \centering
  \includegraphics[width=\columnwidth]{figs/Phase_Diagram_of_P_vs_T_AS}
  %\includegraphics[height=10cm]{figs/Phase_Diagram_of_P_vs_T_AS}
  \caption{Phase Diagram of the reduced pressure verses the reduced temperature. 
  The white line marks the boundary from simulations by Ahmed and Sadus~\cite{ahmedsadus}.}
  \label{fig:Phase_Diagram_P_vs_T_AS}
\end{figure}

Figure~\ref{fig:p-vs-T_at_fixed_density} shows individual plots of the 
reduced pressure versus the reduced temperature at fixed reduced densities 
from $n^*$ = 0.7 to 1.2. As can be seen by comparison with Figure 
\ref{fig:Phase_Diagram_P_vs_T_AS}, the plotted lines display kinks when 
the WCA fluid transistions into a solid. These downward bends align to 
form the curved interface separating the blue and red areas in 
Figures~\ref{fig:Phase_Diagram_P_vs_T} and \ref{fig:Phase_Diagram_P_vs_T_AS}.

\begin{figure}
  \centering
  \includegraphics[width=\columnwidth]{figs/p-vs-T_at_fixed_n_noMC}
  \caption{Plot of the reduced pressure verses the reduced temperature. 
  The lines bending downward indicate freezing.}
  \label{fig:p-vs-T_at_fixed_density}
\end{figure}

>>>>

The goal of this project is to generate temperature-density and 
pressure-temperature phase diagrams for a Weeks-Chandler-Anderson (WCA) 
model fluid using a computer program. 
To do this we need to find the Helmholtz free energies that the fluid
would have in a liquid state, and in a crystalline solid state 
at a given temperature and density. 
%Once the Helmholtz free energy for both the crystal and liquid states of 
%the fluid are found for a given temperature and density, they can be 
%compared to find the resulting state of the fluid. 
Outside the region of 
coexistence which exists between the liquid and crystal states, 
the fluid will be completely in a crystalline state if the 
crystal free energy is lower than the liquid free energy, and it will be 
completely in a liquid state if the liquid free energy is lower than 
the crystal free energy. Maxwell's Double Tangent Construction is used 
to determine the actual number densities of the crystal and liquid states
at the boundaries of the coexistance region for a given temperature from 
which the phase diagrams can be constructed.

%In general, if at some number density and temperature the crystal free energy 
%is lower than the homogeneous free energy of the liquid, then the fluid will 
%be in the crystalline state. If the homogeneous liquid free energy is lower 
%than the crystal free energy, then the fluid will be in the liquid state.

%To find the equilibrium Helmholtz free energies we use classical Density 
%Functional Theory (cDFT) in conjunction with Soft Fundamental Measure Theory (SFMT).
%%the corresponding equilibrium number density profile. 
%In particular,

In general, the Helmholtz free energy can be written as a functional of 
the number density profile $n(\vec{r})$ which describes the way the average number 
density varies spatially. 
\begin{equation}{F[n(\vec{r})]=F_{ideal}[n(\vec{r})] + F_{excess}[n(\vec{r})]}\end{equation} 
Classical Density Functional Theory (cDFT) is used to find the equilbrium 
Helmholtz free energy of the system 
by varying the number density profile $n(\vec{r})$ until the free energy 
is minimized. The minimum free energy, and its corresponding number 
density profile are then the equilibrium values of the Helmholtz free energy
of the system at the given temperature and number density.

To find the Helmholtz free energy both the ideal Helmholtz free energy
and the excess Helmholtz free energy must be found and added together.
The ideal Helmholtz free energy is the free energy the fluid would have in
the absence of any interactomic potential energy $V(r)$ between the spheres, 
or atoms that make up the fluid. The excess Helmholtz free energy is that 
additional energy which results from the presence of an interatomic potential 
energy $V(r)$ between the spheres.
%\begin{equation}{F=F_{ideal} + F_{excess}}\end{equation} 
%For a spatially varying number density, as would be expected for a crystal, 
%the free energy is a functional of the number density profile $n(\vec{r})$  
%The Helmholtz free energy excess free energy is then added to the ideal free energy calculated 
%analytically to find the resulting free energy for the system. 
Soft Fundamental Measure Theory (SFMT) is a method used to form an expression 
for the excess Helmholtz free energy of a particular model fluid without 
having to take explicitly into account the interaction each sphere, or atom, 
has with every other sphere. 
%Classically, fluids have been modeled by a collection of small, 
%impenetrable spheres colliding with one another like billiard balls. 
%In the simplest case, the spheres are treated as having only a replulsive 
%potential. This model, called the Hard-Sphere fluid, has served as the 
%primary reference system for fluids. This is due to the fact that the 
%repulsion between atoms is much stronger than their attraction, and so 
%the repulsive potential, which is descriptive of hard spheres, dominates 
%the interactions between atoms. In 1954 Zwanzig introduced the Square-well 
%fluid which is a perturbation of the Hard-Sphere fluid created by adding 
%a hard-edge attractive potential to the repulsive potential of the 
%Hard-Sphere fluid~\cite{ZwanzigSqrWell}. In 1964 Rowlinson studied 
%spheres with softly fading replusive potentials which he modeled by making
%the radius of the spheres temperature dependent~\cite{rowlinson1964statistical}. 
%This reflects the idea that soft-spheres penetrate more deeply into 
%each other when they collide at higher temperatures. 
%
%In 1967 Barker and Henderson combined the perturabtion approach of Zwanzig 
%with Rowlinson's idea of using temperature-dependent radii to model spheres 
%with soft repulsive potentials to create the Barker-Henderson model 
%fluid~\cite{barker1967perturbation}, where a soft-sphere fluid by is 
%modeled by using a Hard-Sphere fluid with hard spheres of larger radii 
%at low temperatures, and smaller radii at high temperatures. In 1971 Weeks, 
%Chandler, and Anderson used temperature and density dependent hard-sphere 
%radii to model spheres with the more realistic softly fading repulsive 
%portion of the Leonard-Jones potential~\cite{andersen1971relationship}, 
%which is known as the Weeks-Chandler-Anderson model fluid. 
%
%While models for particular fluids were being created, powerful methods 
%to describe the properties of fluids in general were also being developed. 
%In the late 1950s, Scaled Particle Theory (SPT)~\cite{ReissSPT} was 
%introduced from which an equation of state, and an expression for the 
%excess Helmholtz free energy of a homogeneous Hard-Sphere fluid can be 
%obtained~\cite{Hansen}. \color{red}ADD Percus-Yevick introduced an 
%alternative method...OZ... \color{black}
%%Percus and Yevick took another approach to the Hard-Sphere fluid.
%In 1961 Morita and Hiroike introduced a density functional 
%approach~\cite{MoritaDFT} to finding the equilibrium grand free energy 
%(the equilibrium Helmholtz free energy in the case of a canonical 
%ensemble), and the cooresponding equilibrium number density profile for 
%inhomogeneous fluids. To use this approach, a functional must be 
%constructed for a particular fluid.
%%DFT Evans 1979
%%Led by the consistency bewteen results from SPT and Percus-Yevick, 
%In 1989 Rosenfeld introduced Fundamental Measure Theory (FMT)~\cite{rosenfeld1989} 
%(which can be constructed from SPT~\cite{santos2012phi3}) to form a 
%functional for the Hard-Sphere fluid. Tarazona later improved on the 
%method by introducing a tensor version of the functional~\cite{tarazonaphi3, 
%santos2012phi3}, and in 1999 Schmidt adopted FMT for soft spheres 
%forming Soft Fundamental Measure Theory (SFMT)\cite{schmidt1999density}. 
Schmidt applied his Soft Fundamental Measure Theory to various fluids 
with soft repulsive and soft attractive potentials, and developed an erf 
model for spheres with steep, short-range soft repulsive 
potentials~\cite{schmidt2000fluid}.
% like that exhibited by a WCA fluid.

In this paper, classical Density Functional 
Theory will be used to predict the freezing of a Weeks-Chandler-Anderson 
model fluid by applying SFMT with Schmidt's proposed erf model, and our temperature
dependent parameters to form the functional for the excess Helmholtz free energy. 
%for generating the weight funcions, and Tarazona's tensor functional. 
Results will be compared to those generated from Monte-Carlo simulations.

@@

\section{Overview}
The goal of this project is to generate phase diagrams for a 
Weeks-Chandler-Anderson model fluid using a computer program. 
To do this we find the Helmholtz free energies that the fluid
would have at a given temperature and density in a  
liquid state, and in a crystalline solid state. 
%Once the Helmholtz free energy for both the crystal and liquid states of 
%the fluid are found for a given temperature and density, they can be 
%compared to find the resulting state of the fluid. 
Outside the region of 
coexistence which exists between the liquid and crystal states, 
the fluid will be completely in a crystalline state if the 
crystal free energy is lower than the liquid free energy, and it will be 
completely in a liquid state if the liquid free energy is lower than 
the crystal free energy. Maxwell's Double Tangent Construction is used 
to determine the actual number densities of the crystal and liquid states
at the boundaries of the coexistance region for a given temperature, 
and construct phase diagrams.

%In general, if at some number density and temperature the crystal free energy 
%is lower than the homogeneous free energy of the liquid, then the fluid will 
%be in the crystalline state. If the homogeneous liquid free energy is lower 
%than the crystal free energy, then the fluid will be in the liquid state.

%To find the equilibrium Helmholtz free energies we use classical Density 
%Functional Theory (cDFT) in conjunction with Soft Fundamental Measure Theory (SFMT).
%%the corresponding equilibrium number density profile. 
%In particular,

In general, the Helmholtz free energy can be written as a functional of 
the number density profile $n(\vec{r})$ which describes the way the average number 
density varies spatially. 
\begin{equation}{F[n(\vec{r})]=F_{ideal}[n(\vec{r})] + F_{excess}[n(\vec{r})]}\end{equation} 
Classical Density Functional Theory (cDFT) is used to find the equilbrium 
Helmholtz free energy of the system at a given temperature and density
by varying the number density profile $n(\vec{r})$ until the free energy 
is minimized. The minimum free energy, and its corresponding number 
density profile are then the equilibrium values for that temperature 
and number density.

The Helmholtz free energy consists of two parts: the ideal Helmholtz free energy
and the excess Helmholtz free energy.
The ideal Helmholtz free energy is the free energy the fluid would have in
the absence of any interactomic potential energy $V(r)$ between the spheres, 
or atoms that make up the fluid. The excess Helmholtz free energy is that 
additional energy which results from the presence of an interatmoic potential 
energy $V(r)$ between the spheres.
%\begin{equation}{F=F_{ideal} + F_{excess}}\end{equation} 
%For a spatially varying number density, as would be expected for a crystal, 
%the free energy is a functional of the number density profile $n(\vec{r})$  
%The Helmholtz free energy excess free energy is then added to the ideal free energy calculated 
%analytically to find the resulting free energy for the system. 
Soft Fundamental Measure Theory (SFMT) is used to form the expression 
for the excess Helmholtz free energy without having to take explicitly 
into account the interaction each sphere, or atom, has with every other 
sphere.

 ******

@@

@@

\section{Our Functional for the Excess Helmholtz free energy}
In order to apply classical Density Functional Theory, the Helmholtz energy
must be found. Computing the ideal portion of the Helmholtz free energy is
straightforward, but computing the excess portion of the Helmholtz free energy 
is difficult since it depends on the interatomic potential energy $V(r)$ between 
each sphere with all the other spheres. Soft Fundamental Measure Theory is a method
developed to form an expression for the excess Helmholtz free energy without
explicitly taking into account the interaction of each sphere with all the others, 
but it must be taylored to fit a particular fluid. 
%The excess Helmholtz free energy is particular to the fluid being modeled, 
%as it depends on the interatomic potential V(r).

We use Soft Fundamental Measure Theory to form a functional for the excess 
Helmholtz free energy appropriate for the WCA fluid by introducing our 
temperature dependent parameters $\alpha(T)$ and $\Xi(T)$. The functional 
is written in general form as 
\begin{align}
  F_{excess}[n(\vec{r})]=k_BT\int(\Phi_1(\vec{r})+\Phi_2(\vec{r})+\Phi_3(\vec{r}{)) d}\vec{r}
\end{align}
where
\begin{align}
\Phi_1 &= -n_{0}\ln(1-n_{3}) \\
\Phi_2 &= \frac{n_{1}n_{2}-\vec{n_{1}}\cdot\vec{n_{2}}}{1-n_{3}} \\
\Phi_3 &= \frac{{n_2}^3-3n_2\vec{n}_{v2}\cdot\vec{n}_{v2}+\frac{9}{2}[\vec{n}_{v2}\cdot{\overleftrightarrow{n}_{m2}}\cdot{\vec{n}_{v2}}-\operatorname{Tr}({\overleftrightarrow{n}^3_{m2}})]}{24\pi(1-n_3)^2}  
\end{align} 
and Tarazona's tensor expression~\cite{tarazonaphi3, santos2012phi3} is used 
for $\Phi_3$. The weigthed densities $n_0, n_1, n_2,$ and $n_3$ are found from
\begin{equation}{n_i(\vec{r})=\int_{Volume}{n(\vec{r'})w_i(|\vec{r}-\vec{r'}|)d{\vec{r'}}}}\end{equation}
where the number density profile $n(\vec r)$ within the integral is given by a Gaussian function,
%\begin{align}
  %n(\vec r)=(1-f_v)\frac{\exp^{-\frac{r^2}{2{\sigma}^2}}}{\left(\sqrt{2\pi}\sigma\right)^3}
%\end{align}
and the weight functions $w_0, w_1, w_2,$ and $w_3$ are given by
\begin{align}\label{eq:weights}
  w_{0}(r) &=\frac{w_{2}}{4\pi{r}^2} \\
  w_{1}(r) &=\frac{w_{2}}{4\pi{r}} \\
  w_2(r)&=\frac{\sqrt{2}}{\Xi\sqrt\pi}\exp^{-\left(\frac{r-\frac{\alpha}{2}}{\Xi/\sqrt{2}}\right)^2}
  \\
  w_3(r)&=\frac{1}{2}\left[1-\operatorname{erf}\left(\frac{r-\frac{\alpha}{2}}{\frac{\Xi}{\sqrt{2}}}\right)\right]
\end{align}
The weight fucntions $w_{2}(r)$ and $w_{3}(r)$ are constructed using 
Schmidt's proposed erf model~\cite{schmidt2000fluid} in which he set
\begin{equation}{w_3(r)=\frac{1}{2}}\left[1-\operatorname{erf}\left(\frac{r-\frac{\sigma}{2}}{\frac{\text{a}}{\sqrt{2}}}\right)\right]\end{equation} 
where $w_3(r)$ is subject to the boundary conditions $w_3(0)\approx{1}$ 
and $w_3(\infty)=0$. 
%\color{red}These boundary conditions are satisfied for $\Xi{\sqrt{2}<<\alpha}$, or $k_BT << 2.21$. \color{black} 
Our functional is  created by replacing Schmidt's parameters $\sigma$ 
and $a$ with our temperature dependent parameters $\alpha(T)$ and $\Xi(T)$.
\begin{equation}\sigma = \alpha(T)\text{~~~~~~~and~~~~~~~} a = \Xi(T)\end{equation}

@@

The result can be made more accurate by increasing NumPoints which is the 
number of vectors randomly generated. 
%-------Antithetic-------------------
%In order to further reduce the error 
%in the average, antithetic variates are used. Rather than computing an average 
%of a set of random points, each random point in the set is paired with a 
%point along the same line as the first point, but opposite in direction, 
%as shown in Figure \ref{fig:AntitheticVariate}. This reduces first order 
%error in the average by filtering out an erroneous offset of values along 
%the line connecting the two points by averaging the two results, one of 
%which may be erroneously higher than it should be while the other is 
%erronesously lower than it should be.

 %\begin{figure}[h!]
    %\centering
    %\includegraphics[height=4cm]{AntitheticVariate.png}
    %\caption{Antithetic variates reduce first order error in an average. 
    %Each point in the average is paired with another point from along 
    %the same line as the first, and at an equal, but opposite distance.}
    %\label{fig:AntitheticVariate}
  %\end{figure} 
%Incorporating antithetic variates $-\vec{dr}$ for every $\vec{dr}$ equation ?? becomes:
%\begin{displaymath}{n_i(\vec{r}_k, \vec{R}_j)=\sum_{NumPoints}\frac{1}{2}\frac{(1-f_v)\left[w_i(|\vec{r}-\vec{R_j}-\vec{dr}|) +w_i(|\vec{r}-\vec{R_j}+\vec{dr}|)\right]}{NumPoints}}\end{displaymath}   The process is repeated for all the other $\vec{R}_j$'s to get the total weighted densities at vector $\vec{r}_k$ due to all the Gaussians. 
%\begin{displaymath}{n_i(\vec{r}_k)=\sum_j{n_i(\vec{r}_k, \vec{R}_j)}}\end{displaymath}
%Then the entire process repeated for each vector $\vec{r}_k$ to get the 
%total weighted densities $n_i(\vec{r})$ as a function of the position $\vec{r}$.

%The standard error of the mean (SEM) is given by:
%\begin{equation}{SD_{mean}=\frac{SD}{\sqrt{N}}}\end{equation} which gives 
%a measure of the error in $n_3=\overline{w}_3$:
%\begin{equation}{Error=\sqrt{\frac{\overline{w_3^2}-(\overline{w}_3)^2}{NumPoints}}}\end{equation} 
%NumPoints, the number of vectors randomly generated, is increased until:
%\begin{equation}{Error<\frac{|1-n_3|}{4}}\end{equation} where the maximum 
%value that $n_3$ can be without error is 1.

%Figure \ref{fig:GaussandW2_actual} ......

 \begin{figure}[h!]
    \centering
    \includegraphics[height=6cm]{GaussandW2_actual.png}
    \caption{A Gaussian centered at $\vec{R}$ is shown in blue, and a cross-sectional 
    view of $w_2$ centered at $\vec{r}'$ is shown in purple. Here, the weight function 
    is evaluated at $\vec{r}-\vec{r}'$ where $\vec{r}'=\vec{R}+\vec{dr}$ and $\vec{dr}$ 
    is generated randomly according to a Gaussian distribution.} 
  \label{fig:GaussandW2_actual}
  \end{figure}

 \begin{figure}[h!]
    \centering
    %\includegraphics[height=6cm]{GaussandW2_thinkas.png}
    %\caption{An alternative way of viewing Figure \ref{fig:GaussandW2_actual} where 
    %the weight function, shown by the purple dashed lines, is centered at $\vec{r}$  
    %and fixed in place as $\vec{dr}$ varies randomly.} 
  \label{fig:GaussandW2_thinkas}
  \end{figure}

@@

\begin{figure}
  \centering
  %\includegraphics[width=\columnwidth]{figs/Phase_Diagram_of_T_vs_n_AS}
  %\includegraphics[height=10cm]{figs/Phase_Diagram_of_T_vs_n_AS}
  %\caption{Phase Diagram of the reduced temperature verses the reduced density for the WCA fuild. 
  %White lines show the liquid and solid transition densities at each temperature from 
  %simulations of a WCA fluid by Ahmed and Sadus~\cite{ahmedsadus}. The gray region is the region of coexistence.}
  \label{fig:Phase_Diagram_of_T_vs_n_AS}
\end{figure}

@@

\begin{figure}
  \centering
  %\includegraphics[width=\columnwidth]{figs/Phase_Diagram_of_P_vs_T_AS}
  %\includegraphics[height=10cm]{figs/Phase_Diagram_of_P_vs_T_AS}
  %\caption{Phase Diagram of the reduced pressure verses the reduced temperature. 
  %The white line marks the boundary from simulations by Ahmed and Sadus~\cite{ahmedsadus}.}
  \label{fig:Phase_Diagram_P_vs_T_AS}
\end{figure}

%Figure~\ref{fig:p-vs-T_at_fixed_density} shows individual plots of the 
%reduced pressure versus the reduced temperature at fixed reduced densities 
%from $n^*$ = 0.7 to 1.2. As can be seen by comparison with Figure 
%\ref{fig:Phase_Diagram_P_vs_T_AS}, the plotted lines display kinks when 
%the WCA fluid transistions into a solid. These downward bends align to 
%form the curved interface separating the blue and red areas in 
%Figures~\ref{fig:Phase_Diagram_P_vs_T} and \ref{fig:Phase_Diagram_P_vs_T_AS}.

\begin{figure}
  \centering
  %\includegraphics[width=\columnwidth]{figs/p-vs-T_at_fixed_n_noMC}
  %\caption{Plot of the reduced pressure verses the reduced temperature. 
  %The lines bending downward indicate freezing.}
  \label{fig:p-vs-T_at_fixed_density}
\end{figure}
